Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-24 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Sentence corrected

Collaborative IEC systems need to store highly connected data, as it is common in current applications
like social networks. In order to deal with large datasets of connected data found in these systems,
graph databases \cite{angles2012comparison} have been proposed as an alternative to relational databases 
which have performance limitations when dealing with highly connected data \cite{holzschuher2013performance}.
In this work the use of a graph data model for representing the interactive process of C-IEC systems is proposed.
Moreover, an proof-of-concept implemantation of IEC incorporating the graph model to the evolutionary algorithm is presented.
%Finally, a comparasion of between three deployments of the system, with different increase the collaboration of volunteers.

@@

Only the "Start a session" and "Explore collections of other friends". 
Are not found in the graph model, these are stored in the PostgreSQL relational
database system.

>>>>

Collaborative IEC systems need to store highly connected data, as it is common in current applications
like social networks. In order to deal with large datasets of connected data found in these systems,
graph databases \cite{angles2012comparison} have been proposed as an alternative to relational databases 
which have performance limitations when dealing with highly connected data \cite{holzschuher2013performance}.
In this work the use of a graph data model for representing the interactive process of C-IEC systems is proposed.
Moreover, an proof-of-concept implemantation of IEC incorporating the graph model to the evolutionary algorithm is presented.

%Finally, a comparasion of between three deployments of the system, with different increase the collaboration of volunteers.

@@

Only the ``Start a session'' and ``Explore collections of other friends'' actions 
are not found in the graph model as these are stored in the PostgreSQL relational
database system.
